Meta RL analyses

### 2019-02-26 meta_RL_analyses.Rmd
Analysis updates/new results

result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   "language", "language_noncompositional", "language_simplified", "language_random_holdout", "language_meta")

@@

```{r}
language_d = load_d(results_dir, c("language", "language_simplified", "language_random_holdout", "language_meta", "language_noncompositional"), num_runs, "new_language_rewards")

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
                               #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
                               "language", "language_random_holdout", "language_simplified", "language_meta"
                               ), num_runs, "new_meta_true_losses")

@@

```{r}
lang_meta_d = load_d(results_dir, c("language_meta", "language_simplified"
                               ), num_runs, "new_language_meta_true_losses")

>>>>

result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout")

@@

```{r}
language_d = load_d(results_dir, c("language", "language_noncompositional", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"), num_runs, "new_language_rewards")

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
                               #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
                               "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"
                               ), num_runs, "new_meta_true_losses")

@@

```{r}
lang_meta_d = load_d(results_dir, c(
                               "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", "language_simplified_random_holdout"
                               ), num_runs, "new_language_meta_true_losses")
